A new method to estimate dark matter halo concentrations

### 2015-09-28 paper/article.tex
nuevo parrafo en conclusiones, nuevo orden de las graficas, nuevo apendice

@@

\subsection{Tests on Mock Halos}

@@

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20.pdf}
  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20000.pdf}
\caption{Cumulative distribution of the fractional difference, $D$, between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with an input concentration in a different range for
  a number of particles $N=20$ (right panel) and $N=20000$ (left panel).
    \label{fig:results_mocks_conc}}
\end{figure*}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{error.pdf}
\end{center}
\caption{Average value of the relative error in the concentration
  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
  the set of mock halos. Different symbols represent different
  methods. Our method provide the most accurate estimate at fixed
  particle number $N$.
    \label{fig:error}}
\end{figure}

\subsection{Tests on N-body data}
\label{sec:data}
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.33\textwidth]{mass-velocity.pdf}
    \includegraphics[width=0.33\textwidth]{mass-density.pdf}
    \includegraphics[width=0.33\textwidth]{density-velocity.pdf}
  \end{center}
  \caption{Comparison between the concentrations measured by our
    method and the maximum velocity (left) and density (middle)
    methods. The line indicates the equal value between the two
    techniques. The right panel compares the results of the maximum
    velocity and density methods.
  \label{fig:mdv}}
\end{figure*}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.90\textwidth]{concentration.pdf}
\end{center}
\caption{Mass-concentration relationship for the three different
  methods used on the same cosmological N-body data. The central lines
  correspond the median and the shadowed region indicates the
  quartiles.
    \label{fig:concentration}}
\end{figure*}

@@

Comparison against other methods.\\

@@

>>>>

\begin{figure*}
\begin{center}
  \includegraphics[width=0.75\textwidth]{error.pdf}
\end{center}
\caption{Average value of the relative error in the concentration
  estimate, $\avg{|D|}$, as a function of the particle number $N$ in
  the set of mock halos. Different symbols represent different
  methods. Our method provide the most accurate estimate at fixed
  particle number $N$.
    \label{fig:error}}
\end{figure*}

@@

\subsection{Mock Halos}

@@

\begin{figure}
  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20.pdf}
  \includegraphics[width=0.45\textwidth]{mock_percentual_diff_conc_20000.pdf}
\caption{Cumulative distribution of the fractional difference, $D$, between
  the input concentration in the mock halo generator, $c_{in}$ and the
  measurement by our MCMC code, $c_{out}$. Each curve corresponds to
  halos generated with an input concentration in a different range for
  a number of particles $N=20$ (right panel) and $N=20000$ (left panel).
    \label{fig:results_mocks_conc}}
\end{figure}

@@

\subsection{N-body data}
\label{sec:data}
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.33\textwidth]{mass-velocity.pdf}
    \includegraphics[width=0.33\textwidth]{mass-density.pdf}
    \includegraphics[width=0.33\textwidth]{density-velocity.pdf}
  \end{center}
  \caption{Comparison between the concentrations measured by our
    method and the maximum velocity (left) and density (middle)
    methods. The line indicates the equal value between the two
    techniques. The right panel compares the results of the maximum
    velocity and density methods.
  \label{fig:mdv}}
\end{figure*}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.75\textwidth]{concentration.pdf}
\end{center}
\caption{Mass-concentration relationship for the three different
  methods used on the same cosmological N-body data. The central lines
  correspond the median and the shadowed region indicates the
  quartiles.
    \label{fig:concentration}}
\end{figure*}

@@

The first benchmark was performed on mock halos generated with known
concentration values for different particle numbers. 
For all methods, the accuracy in retrieveing the input concentration
increases with the number of particles as summarized in Figure \ref{fig:error}.
Our method systematically shows smaller errors in the retrieved values
compared to the other two methods, going from $10\%$ for halos with
$20$ particles down to $0.01\%$ for halos with $2\times 10^4$ particles. 
In our method the average error on the retrieved values decreases with
the number of particles as $\langle|D|\rangle\propto N^{-1}$.
The error in density method initially behaves as $\langle|D|\rangle\propto
N^{-3/2}$ but at $N=2\times 10^3$ it saturates to $0.1\%$. 
For the velocity method the error behaves closely to
$\langle|D|\rangle\propto N^{-1/2}$

@@

\appendix
